Incentives are the biggest barriers to widespread data sharing

### 2021-08-04 new-paper.Rmd
added some further clarity on audience and how our work is different to the other papers

As academic data scientists, we spend considerable time cleaning messy data and believe that preparing data for easy reuse can be a catalyst to improve the quality of data and pave the way for other incentives such as community adoptions, which will then create the culture change needed to credit data similar to publications. In this note, we describe a set of practices that researchers can adopt to make data more useful in the context of reproducibility. It should not be a huge burden to share data in a format that is readily usable by others. And similarly, this burden should be reduced by those who want to use another's data.

>>>>

We believe a key audience could be better served by the current literature on data sharing: researchers who have finished data analysis on tabular data, are ready to submit for publication.
Many papers provide rules and guidelines for sharing data, such as providing metadata, citation, licenses, and lists of data repositories to use. These papers provide general advice from the ethical considerations of sharing data [@Moles2013], how to share many different data types (images, video, etc) [@Hart2016], to “Reward Colleagues Who Share Their Data Properly” [@Goodman2014]. There is also specific advice like the importance of very clean and properly shaped data [@White2013], and to use open source software with changes tracked [@Boland2017]. These papers do not discuss the approach of sharing data within software, which has seen a rise in the use of research compendiums (e.g, [@Marwick2018]). Across many of these articles there is common advice that is useful, but individually, their advice is too general or specific for our audience.

As academic data scientists, we spend considerable time cleaning messy data and believe that preparing data for easy reuse can be a catalyst to improve the quality of data and pave the way for other incentives such as community adoptions, which will then create the culture change needed to credit data similar to publications. In this paper, we describe a set of common sense practices that researchers can adopt to make data more useful in the context of reproducibility. It should not be a huge burden to share data in a format that is readily usable by others. And similarly, this burden should be reduced by those who want to use another's data.
